%
% Simple Latex 2e template
%
\documentclass[12pt]{article}
\usepackage[usenames,dvips]{pstcol}
\usepackage{color}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{footnote}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{array,multirow}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{epstopdf}

\setcounter{secnumdepth}{4}
%\titleformat{\paragraph}
%{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
%\titlespacing*{\paragraph} {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
%
\include{symbols}
%
\textwidth 6.5in
\textheight 9.5in
\topmargin -0.6in
\oddsidemargin 0.0in
\evensidemargin 0.0in
\parindent 0.5in
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
%
\def\baselinestretch{1.0}
%
\newcommand{\smaller}{\fontsize{8}{12}\selectfont}
\newrgbcolor{maroon}{.45 0.1 0.1}
%
% Try making it behave with figures
%
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}
%
\begin{document}
\pagestyle{plain}
\begin{flushright}
Version 1.0\\
\today\\
HJF\\
\end{flushright}
%
% Title

Proposed List of Figures (work-in-progress- please edit, add, or delete):

\begin{enumerate}
%\setlength{\itemsep}{-0.03in}
\item An artist's rendition of bunched neutrinos, created by protons
with a 500 MHz RF structure, traversing a large detector.


\item Current Fermilab LBNF physical layout (target/horn, decay region, near
and far detectors).


\item Current Fermilab 53 MHz RF structure and proposed 500 (530?) MHz structure.

\item Current 53 Fermilab RF cavity and proposed 500 (530?) MHz RF
Cornell-B? cavity.

\item The width of the proton bunch after re-bunching as a function of
adiabatic time constant for turning on the higher frequency RF.

\item The fractional effective loss of protons on target (POT) 
due to the longer cycle time as a function of the adiabatic time
constant for turning on the higher frequency RF; (do we include the
time to turn down the 53MHz, or is this included already?).

\item The distribution of proton intensity in one bunch after a 500 MHz RF
re-bunching, assuming a reduction of no more than 5\% of POT due to the longer
acceleration cycle.

\item Distributions of the number of events versus time relative to
  the proton bunch of e, mu, and tau neutrinos and anti-neutrinos for
  a delta-function proton bunch and Forward Horn Current (FHC) . The
  distributions are shown for five energy bins in addition to the
  total.

\item Distributions of the number of events versus time relative to
  the center of the proton bunch of e, mu, and tau anti-neutrinos and
  neutrinos for a delta-function proton bunch and Reverse Horn Current
  (RHC).  The distributions are shown for five energy bins in addition
  to the total.

\item Distributions of the number of events versus time relative to
  the center of the proton bunch of e, mu, and tau neutrinos and
  anti-neutrinos for Forward Horn Current (FHC) assuming the current
  53 MHz RF bunch structure.

\item Distributions of the number of events versus time relative to
  the center of the proton bunch of e, mu, and tau anti-neutrinos and
  neutrinos for Reverse Horn Current (RHC) assuming a 500 MHz RF bunch
  structure.

\item Fractions of e, mu, and tau neutrinos and anti-neutrinos in 50
(upper-right panel), 100 (upper-left), 250(lower-left), and 500
(lower-right) psec bins relative to a delta-function proton bunch.

\item Fractions of e, mu, and tau neutrinos and anti-neutrinos captured
in 50 psec (upper-right panel), 100 psec (upper-left), 250
psec(lower-left), and 500 psec (lower-right) bins relative to a
delta-function proton bunch.

\item Fractions of e, mu, and tau neutrinos and anti-neutrinos
  captured in 50 psec (upper-right panel), 100 psec (upper-left), 250
  psec(lower-left), and 500 psec (lower-right) time bins with a 500
  MHz RF structure. The binning is such that the central bin is
  centered on the peak of the proton bucket distribution (it's late
  and I'm muddled- this will need fixing- HJF).

\item Fraction of `wrong-sign' anti-neutrino background in e, mu, and
tau neutrinos for Forward Horn Current captured in 50 psec
(upper-right panel), 100 psec (upper-left), 250 psec(lower-left), and
500 psec (lower-right) time bins with a 500
MHz RF structure. The binning is such that the central bin is
  centered on the peak of the proton bucket distribution.


\item Fraction of `wrong-sign' neutrino background in e, mu, and tau
  anti-neutrinos for Reverse Horn Current captured in 50 psec
  (upper-right panel), 100 psec (upper-left), 250 psec(lower-left),
  and 500 psec (lower-right) bins with a 500 MHz RF structure. The
  binning is such that the central bin is centered on the peak of the
  proton bucket distribution.



\end{enumerate}
\end{document}
